DH Min's Machine Learning Project : 2014 Dec 20
========================================================
## 0. Summary 
### This is a report describing how to build a human activity recoginition model with weight lifting exercise data provided by Groupware(http://groupware.les.inf.puc-rio.br/har) 
### The human activity recognition model which predicts/classify weight lift activities, is built using 'gbm'method. 

## 1. Data
### For details of the data, refer the Groupware url.   
### The training data and test data for this project are provided by instructor 
### https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv
### https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

## 2. Model building process
### Load necessary packages
```{r}
library(caret)
library(AppliedPredictiveModeling)
```
### read training data file and test data file
```{r}
training <- read.csv("./pml-training.csv")
testing <- read.csv("./pml-testing.csv")
```
### delete meaningless columns,which filled with 'NA',from testing data.
```{r}
testing <- testing[,colSums(is.na(testing))<nrow(testing)]
```
### delete training data columns which are not used in testing data. Keeping 'classe' column.
```{r}
training <- subset(training, select = -c(X))
testing <- subset(testing, select = -c(X))
selectedColnames <- colnames(testing)
selectedColnames <- c(selectedColnames, "classe")
training <- training[ , which(names(training) %in% selectedColnames)]
```
### fitting a model with 'gbm'method. I chose 'gbm'method because it is a method that can be suitable for multi variable classification, well-known for being comparatively fast and accurate since it uses trees and boost for prediction.
```{r}
modelFit <- train(classe ~., data=training, method = "gbm")
```
## 3. Model  
### Seems the model is reliable, it took a long time to learn but it shows very good accuracy and expected out of sample error rate is less than 1%.
```{r}
modelFit
```
### Visualized the model's feature
```{r fig.width=7, fig.height=6}
plot(modelFit)
```
```{r fig.width=7, fig.height=6}
plot(modelFit, metric = "Kappa")
```
```{r fig.width=7, fig.height=6}
plot(modelFit, plotType = "level")
```
```{r fig.width=7, fig.height=6}
resampleHist(modelFit)
```

## 4. Prediction
## predict with the model
```{r}
predictions <- predict(modelFit, newdata = testing )
predictions
```



